\chapter{Symmetry, Invariance, and Conservation for Free Fields}
\section{Symmetry Mathematically}
The transformation depicted in Fig. (\ref{fig:cylinder-rot}) can be can be understood either as a rotation of the cylinder in one direction while we remain fixed (an \textbf{\underline{active transformation}}, by name), or alternatively, as a rotation of our viewing frame of reference in the other direction while the cylinder remains fixed (a\underline{ \textbf{passive transformation}}).
\begin{figure}[H]
    \centering
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Can [id:dp6111663527038986] 
\draw   (154,122) -- (154,174) .. controls (154,178.97) and (140.57,183) .. (124,183) .. controls (107.43,183) and (94,178.97) .. (94,174) -- (94,122) .. controls (94,117.03) and (107.43,113) .. (124,113) .. controls (140.57,113) and (154,117.03) .. (154,122) .. controls (154,126.97) and (140.57,131) .. (124,131) .. controls (107.43,131) and (94,126.97) .. (94,122) ;
%Straight Lines [id:da6016989853853066] 
\draw    (124,124) -- (124,76) ;
%Straight Lines [id:da7742642520386162] 
\draw    (124,231) -- (124,183) ;
%Shape: Can [id:dp6333770541501842] 
\draw   (257,122) -- (257,174) .. controls (257,178.97) and (243.57,183) .. (227,183) .. controls (210.43,183) and (197,178.97) .. (197,174) -- (197,122) .. controls (197,117.03) and (210.43,113) .. (227,113) .. controls (243.57,113) and (257,117.03) .. (257,122) .. controls (257,126.97) and (243.57,131) .. (227,131) .. controls (210.43,131) and (197,126.97) .. (197,122) ;
%Straight Lines [id:da2230680788551479] 
\draw    (227,124) -- (227,76) ;
%Straight Lines [id:da2565843946616415] 
\draw    (227,231) -- (227,183) ;

% Text Node
\draw (125,249) node   [align=left] {Unrotated};
% Text Node
\draw (228,252) node   [align=left] {Rotated};
% Text Node
\draw (127,61) node   [align=left] {Axis of symmetry};


\end{tikzpicture}
    \caption{Symmetry of a cylinder}
    \label{fig:cylinder-rot}
\end{figure}
Mathematically, when we change our position of observation, it is equivalent to using a new, different reference frame and coordinate system, oriented differently from, and/or displaced relative to, the original. So a transformation can be viewed simply as a change of coordinate system, and this is often represented as a shifting from unprimed to primed coordinates. In QFT, \textbf{we will focus on passive transformation interpretation.}

\begin{example}
Consider the function 
\begin{equation}
g\left(x^{1}, x^{2}\right)=\left(x^{2}\right)^{2}
\end{equation}
if we have the following rorational transformation as
$$
\left[\begin{array}{l}
{x^{\prime 1}} \\
{x^{\prime 2}}
\end{array}\right]=\underbrace{\left[\begin{array}{cc}
{\cos \theta} & {\sin \theta} \\
{-\sin \theta} & {\cos \theta}
\end{array}\right]}_T\left[\begin{array}{l}
{x^{1}} \\
{x^{2}}
\end{array}\right]
\quad
\left[\begin{array}{l}
{x^{1}} \\
{x^{2}}
\end{array}\right]=\underbrace{\left[\begin{array}{ll}
{\cos \theta} & {-\sin \theta} \\
{\sin \theta} & {\cos \theta}
\end{array}\right]}_{T^{-1}=T^T}\left[\begin{array}{l}
{x^{\prime1}} \\
{x^{\prime2}}
\end{array}\right]
$$
we can express the function in the primed coordinate as:
$$
g=\left(x^{2}\right)^{2}=\left(x^{\prime 1} \sin \theta+x^{\prime 2} \cos \theta\right)^{2}=\left(x^{\prime 1}\right)^{2} \sin ^{2} \theta+\left(x^{\prime 2}\right)^{2} \cos ^{2} \theta+2 x^{\prime 1} x^{\prime 2} \sin \theta \cos \theta \neq\left(x^{\prime 2}\right)^{2}
$$
The transformed form of $g,$ represented by $g^{\prime}$, has the same value at the same physical point, but it is not the same form in terms of the primed coordinates as $g$ was in terms of the unprimed coordinates. But $f^{\prime},$ the transformed form of $f,$ did have the same form in terms of both sets of coordinates, and thus, we dropped the prime on $f$ on the RHS.

In spite of its non-symmetry under rotation, $g$ is symmetric under a different kind of Fransfort of the firc-symment ander founding $f$ the bynaced relative to the first along transformation, the translation to a coordinate system which is displaced relative to the first along the $x^{1}$ axis, i.e., $x^{1} \rightarrow x^{1}=x^{1}+$ constant $,$ or
$$
\left[\begin{array}{l}
{x^{\prime 1}} \\
{x^{\prime 2}}
\end{array}\right]=\left[\begin{array}{l}
{x^{1}} \\
{x^{2}}
\end{array}\right]+\left[\begin{array}{l}
{K} \\
{0}
\end{array}\right] \quad K=\text { constant }
$$
Substitution yields $g^{\prime}$ have the same form.
\end{example}
\begin{qt}
    From the example above, we can deduce the general rule that if a coordinate is missing in a given function, that function is invariant under a transformation solely in the direction of that coordinate (and also under multiplication of the coordiante by a constant).
\end{qt}
\textbf{\redp{So under any transformation of coordinate axes, the value at a physical point of every possible scalar function is invariant.}}
\subsection{Scalar are invariant, vectors are covariant}
\textbf{The scalar value at the point ( equal to the length of the position vector at that point) is the same in both systems, but the coordinate values are not.} For a 2D position vector in physical space, we have
$$
|x|=\left|x^{i}\right|=\sqrt{\left(x^{1}\right)^{2}+\left(x^{2}\right)^{2}}=\sqrt{\left(x^{\prime1}\right)^{2}+\left(x^{\prime2}\right)^{2}}=\left|x^{\prime i}\right|
$$
It is generally true of every vector $\mathbf{v},$ not just the position vector shown here, that its physical, measurable length (a scalar value) remains unchanged under any coordinate transformation, but its component values change. This is called covariance. Scalar values are invariant under coordinate transformation; vector components are \textbf{covariant}.
\begin{qt}
    General rule: if a function $h$ is not a function of the $j$th coordinate $x^j$, then h is symmetric under the transformation $x^{j} \rightarrow x^{j}+$ constant.
\end{qt}
\section{Symmetry in Classical Mechanics}
Recall that a Galilean transformation is
$$
\left[\begin{array}{c}
{x^{1}} \\
{x^{2}} \\
{x^{3}}
\end{array}\right] \rightarrow\left[\begin{array}{c}
{x^{11}} \\
{x^{\prime 2}} \\
{x^{3}}
\end{array}\right]=\left[\begin{array}{c}
{x^{1}-v^{1} t} \\
{x^{2}-v^{2} t} \\
{x^{3}-v^{3} t}
\end{array}\right]
$$
Newtonian mechanics is invariant under the Galilean transformation. But \textbf{Maxwell's eqs are not invariant under Galilean transformation. Instead, it is invariant under Lorentz transformation}
\begin{qt}
    \begin{equation}
\left[\begin{array}{c}
{x^{0}} \\
{x^{1}} \\
{x^{2}} \\
{x^{3}}
\end{array}\right] \rightarrow\left[\begin{array}{c}
{x^{\prime 0}} \\
{x^{\prime 1}} \\
{x^{\prime 2}} \\
{x^{\prime 3}}
\end{array}\right]=\left[\begin{array}{c}
{\gamma\left(x^{0}-\frac{v}{c} x^{1}\right)} \\
{\gamma\left(x^{1}-\frac{v}{c} x^{0}\right)} \\
{x^{2}} \\
{x^{3}}
\end{array}\right]=\underbrace{\left[\begin{array}{cccc}
{\gamma} & {-\gamma \frac{v}{c}} & {0} & {0} \\
{-\gamma \frac{v}{c}} & {\gamma} & {0} & {0} \\
{0} & {0} & {1} & {0} \\
{0} & {0} & {0} & {1}
\end{array}\right]}_{\Lambda}\left[\begin{array}{c}
{x^{0}} \\
{x^{1}} \\
{x^{2}} \\
{x^{3}}
\end{array}\right]
\label{lorentz-trans}
\end{equation}
where
$$
\gamma=\frac{1}{\sqrt{1-\frac{v^{2}}{c^{2}}}} \quad v=v^{1}
$$
\end{qt}
The index notation for Lorentz transformations is 
\begin{qt}
    \begin{equation}
x^{\prime \mu}=\Lambda^{\mu}{}_{v} x^{v} \quad V^{\prime \mu}\left(x^{\prime \alpha}\right)=\Lambda^{\mu}{}_{v} V^{v}\left(x^{\alpha}\right) \quad T^{\prime \mu v}\left(x^{\prime \alpha}\right)=\Lambda^{\mu}{}_{\delta} \Lambda^{v}{}_{\gamma} T^{\delta \gamma}\left(x^{\alpha}\right)
\end{equation}
Note that $\Lambda^{-1},$ the inverse of $\Lambda,$ can be obtained by taking $\mathbf{v} \rightarrow-\mathbf{v}$ since each coordinate system seems to be going in the opposite direction with respect to the other. $\Lambda^{-1}$ will transform $x^{\prime \mu}$ back into $x^{\mu}$.
\end{qt}
\bluep{Recall that the length of a vector in 3D is unchanged under a coordinate system transformation, 1.e., the length 1s a scalar and thus invariant. The same thing is true in 4D for four-vectors.}
$$
w_{\mu} w^{\mu}=w_{0} w^{0}+w_{1} w^{1}+w_{2} w^{2}+w_{3} w^{3}=w^{0} w^{0}-w^{1} w^{1}-w^{2} w^{2}-w^{3} w^{3}=\text { scalar invariant }
$$
\textbf{and that this is the same for any observer in any inertial coordinate system. This applies to any
vector, be it a position vector like $x^{\mu},$ the differential of position $d x^{\mu},$ the four-velocity $u^{\mu}$, the four potential $A^{\mu}$, the partial derivative $\partial^{\mu}$, or any other}.For instance,
$$
\frac{\partial}{\partial x^{\mu}} \frac{\partial}{\partial x_{\mu}}=\partial_{\mu} \partial^{\mu}=\frac{\partial}{\partial x^{0}} \frac{\partial}{\partial x^{0}}-\frac{\partial}{\partial x^{1}} \frac{\partial}{\partial x^{1}}-\frac{\partial}{\partial x^{2}} \frac{\partial}{\partial x^{2}}-\frac{\partial}{\partial x^{3}} \frac{\partial}{\partial x^{3}}=\text { scalar invariant derivative, }
$$
So if X represents a quantity, we have
$$
\frac{\partial}{\partial x^{\mu}} \frac{\partial}{\partial x_{\mu}}=\frac{\partial}{\partial x^{\prime \mu}} \frac{\partial}{\partial x_{\mu}^{\prime}} \rightarrow \frac{\partial}{\partial x^{\mu}} \frac{\partial}{\partial x_{\mu}} X=\frac{\partial}{\partial x^{\prime\mu}} \frac{\partial}{\partial x_{\mu}^{\prime}} X
$$
\subsection{Poincare transformation}
The most general transformation we could have in spacetime would comprise 1) a 4D translation(translating our coordinate axes in space, time, or both), 2) a rotation in space, and 3) a Lorentz transformation to a frame with different relative velocity. (We ignore reflection.)

The rotation in 3D is the same. It does allow us to rotate our 3D axes, however, so that the relative velocity between our original and transformed systems is along the $x^1$ axes of both. \textbf{This lets us use the Lorentz transformation in its simplest form (\ref{lorentz-trans})}. With this form we state the general transformation between coordinate systems, know as \redp{\textbf{Poincare transformation}} as
\begin{equation}
x^{\mu}=\Lambda_{\nu}^{\mu}\left(x^{\nu}+a^{\nu}\right) \quad a^{\nu}=\mathrm{constant} \text { four vector }
\label{poincare-trans}
\end{equation}

\subsection{Other kinds of symmetry}
Consider the Euler-Lagrange equation for a particle in Newtonian mechanics
$$
\frac{d}{d t}\left(\frac{\partial L}{\partial \dot{x}^{i}}\right)-\frac{\partial L}{\partial x^{i}}=0 \quad L=T-V \quad p_{i}=\frac{\partial L}{\partial \dot{x}^{i}}
$$
If the Lagrangian $L$ is not an explicit function of the spatial coordinate $x^i,$ then $\partial L / \partial x^{i}=0$ on the LHS above. Thus, the time derivative of $p_{i}$ is zero.
$$
\frac{d}{d t}\left(\frac{\partial L}{\partial \dot{x}^{i}}\right)=\frac{d p_{i}}{d t}=0 \quad \text { with } \frac{\partial L}{\partial x^{i}}=0 \quad \text { when } \quad L \neq L\left(x^{i}\right)
$$
Hence $p^i$ is constant and thus, conserved. This makes sense since the only source for spatial dependence in $L$ is the potential energy $V$. If we have no $V$ dependence on $x^i$, then there is no force in the $x^i$ direction, and momentum $p_i$ is constant.\textbf{Note this means the Lagrangian is symmtric.}

\redp{If the Lagrangian is symmetric in a coordinate, then the conjugate momentum for that coordiante is conserved.}

\section{Transformations in QFT}
\subsection{Spinor transformation}
For spinor, we seek a matrix which is four by four in spinor space and which represents what ha~pens to a spmor under a Lorentz transformation and/or a rotation of coordinates. That is, we seek D in
\begin{equation}
\psi^{\prime}\left(x^{\prime \mu}\right)=D \psi\left(x^{\mu}\right) \quad \frac{\text { with spinor indices }}{\text { written out }} \quad \psi_{\alpha}^{\prime}\left(x^{\prime \mu}\right)=D_{\alpha \beta} \psi_{\beta}\left(x^{\mu}\right)
\end{equation}
The spinor transformation under Lorentz and rotation transformation is
\begin{equation}
D=e^{-i(\mathbf{L} \mathbf{\Theta}+\mathbf{M} \mathbf{Q})} \quad L^{k}=-\frac{i}{2} \varepsilon_{i j}^{k} \gamma^{i} \gamma^{j}, \quad \Theta^{k}=\left(\theta^{1}, \theta^{2}, \theta^{3}\right), M^{k}=\frac{i}{2} \gamma^{0} \gamma^{k}, Q^{k}=\left(v^{1}, v^{2}, v^{3}\right)
\end{equation}
where $\Theta^{k}$ represents rotation angles of the primed system with respect to the unprimed system; $Q^k$ is a three vector of the boost velocities; and $\epsilon_{ij}{}^{k}$ is zero unless $i,j,k$ are all different, 1 if $ijk=123,231,312$, and -1 for the others.

Note that in formal mathematical language, the set of all possible Lorentz transformations (all possible v) is known as the Lorentz group. When the Lorentz group acts on the coordinate system, it changes what our spinors look like in the new system and this change is represented by $D$. So, \textbf{$D$ is called a representation of the Lorentz group.} It "represents" that group in spinor space.
\begin{qt}
    $\bar{\psi} \psi=$ world scalar $\quad \bar{\psi} \gamma^{\mu} \psi=$ transforms like four vector.
\end{qt}
\section{Lorentz Symmetry of the Lagrangian Density}
Lagrangian Density is symmetric under Lorentz transformation. We conclude this because of Einstein's postulate that the laws of nature (the field equation here) is invariant in form under Lorentz transformation. The Euler-Lagrange equation for fields, which is another form of the field equation, is a law of nature and must, therefore be invariant in form as well.

\section{Noether's Theorem}
There are other ways the Lagrangian density can be symmetric, for example
\begin{equation}
\phi \rightarrow \phi^{\prime}=\phi e^{-i \alpha}
\label{phase-trans}
\end{equation}
and for free scalar field, we have
$$
\mathcal{L}_{0}^{0}=\partial_{v} \underbrace{\phi^{r+} e^{-i \alpha}}_{\phi^{\dagger}} \partial^{v} \underbrace{\phi^{\prime} e^{i a}}_{\phi}-\mu^{2} \underbrace{\phi^{\prime} e^{-i \alpha}}_{\phi^{\dagger}} \underbrace{\phi^{\prime} e^{i \alpha}}_{\phi}=\mathcal{L}_{0}^{0}\left(\phi^{\prime\dagger}, \phi^{\prime}\right)
$$
\subsection{Internal and external symmetries}
Poincaré transformations (Lorentz plus $4 \mathrm{D}$ translation) and $3 \mathrm{D}$ rotations involve changes $\mathrm{t}$ to physical coordinates $x^{\mu}$ of our external world and are called \textbf{external transformations}.

Transformation like (\ref{phase-trans}) have nothing to do with $x^{\mu}$, but instead function in hidden spaces, behind the scene, like Hilbert or Fock space. They are called \textbf{internal transformation}.
\begin{qt}
   Noether's theorem in words: \textbf{ A symmetry in the Lagrangian density implies an associated quantity is conserved.}
   
   Mathematically:If the Lagrangian density $\mathcal{L}\left(\phi^{r}, \phi^{r}, \mu\right)$ is symmetric in form with respect to a transformation in $\phi^{r}$ which is a function of parameter $\alpha$,i.e., $\phi^{r}\left(x^{\mu}\right) \rightarrow \phi^{r}\left(x^{\mu}, \alpha\right)$ then the four current (using $\left.\phi^{r}\left(x^{\mu}, \alpha\right)\right)$
   \begin{equation}
j^{\mu}\left(\phi^{r}, \phi_{, \nu}^{r}\right)=\frac{\partial \mathcal{L}}{\partial \phi_{, \mu}^{r}} \frac{\partial \phi^{r}}{\partial \alpha} \quad(\text { sum on } r)
\end{equation}
bas zero four-divergence,$\partial_{\mu} j^{\mu}=0$. Thus, its zeroth component $j^0$ integrated over all the space is conserved, as is $q j^{0}$ integrated over all space, where $q$ is a constant.
\end{qt}
\subsection{Apply Noether's theorem to free scalar field}
$$
\frac{\partial \mathcal{L}_{0}^{0}}{\partial \phi_{\mu}}=\frac{\partial}{\partial \phi_{, \mu}}\left(\phi_{, \nu}^{\dagger} \phi^{\nu}-\mu^{2} \phi^{\dagger} \phi\right)=\frac{\partial}{\partial \phi_{\mu}}\left(\phi_{, \mu}^{\dagger} \phi^{\nu}\right)
=\frac{\partial \phi_{, \nu}^{\dagger}}{\partial \phi_{\mu}} \phi^{,\nu}+\phi_{, \nu}^{\dagger} \frac{\partial \phi^{,\nu}}{\partial \phi_{,\mu}}=\phi_{, \nu}^{\dagger} g^{\nu \mu}=\phi^{\dagger, \mu}
$$
$$
\frac{\partial \mathcal{L}_{0}^{0}}{\partial \phi^{\dagger}, \mu}=\frac{\partial}{\partial \phi^{\dagger}, \mu}\left(\phi_{, \nu}^{\dagger} \phi^{\nu}-\mu^{2} \phi^{\dagger} \phi\right)=\frac{\partial}{\partial \phi^{\dagger}}\left(\phi^{\dagger}, \phi^{,\nu}\right)=\frac{\partial \phi^{\dagger}_{, \nu}}{\partial \phi^{\dagger}_{, \mu}} \phi^{,\nu}=\delta_{v}^{\mu} \phi^{, v}=\phi^{,\mu}
$$
and
$$
\begin{array}{l}
{\frac{\partial \phi\left(x^{\eta}, \alpha\right)}{\partial \alpha}=\frac{\partial}{\partial \alpha} \phi\left(x^{\eta}\right) e^{-i \alpha}=-i \phi\left(x^{\eta}\right) e^{-i \alpha}} \\
{\frac{\partial \phi^{\dagger}\left(x^{\eta}, \alpha\right)}{\partial \alpha}=\frac{\partial}{\partial \alpha} \phi^{\dagger}\left(x^{\eta}\right) e^{i \alpha}=i \phi^{\dagger}\left(x^{\eta}\right) e^{i \alpha}}
\end{array}
$$
Using the relation above, we have
$$
j^{\mu}\left(\phi^{r}, \phi^{r}_{,v}\right)=i\left(\phi^{,\mu}\left(x^{\eta}\right) \phi^{\dagger}\left(x^{\eta}\right)-\phi^{\dagger, \mu}\left(x^{\eta}\right) \phi\left(x^{\eta}\right)\right)
$$
This is identical to the scalar four-current.\redp{The expectation value ( expected measurement) of a conserved operator is conserved. If the state measured is in an eigenstate, any measurement at any time will yield the same eigenvalue}.
\section{Symmetry, Gauges, and Gauge theory}
\begin{itemize}
    \item \textbf{Gauge invariance }(or gauge symmetry) is the property of a field theory in which different configurations of the underlying fundamental, but unobservable, field(s) result in identical observable properties.
    \item the unobservable field, often a potential field, is called the\textbf{ gauge field}.
    \item A gauge transformation changes the gauge field from one configuration to another. \redp{Each different configuration of the gauge field is a different gauge.}
    \item A theory have gauge invariance (symmetry) is called a gauge theory.
\end{itemize}
\redp{\textbf{We can also say that a gauge theory is a type of field theory in which the Lagrangian ( density) is invariant under a continuous (not discrete) transformation.}}
\section{A Solved Exercise}
\textbf{Problem 14.} Show that the total (not density) 3-momentum $k^{i}$ for free scalars is conserved. Use our knowledge that the conjugate momentum for $x^{i}$ is $k_{i}$, the total (not density) 3 -momentum (expressed in covariant components), and it is conserved if $L$ is symmetric (invariant) under the coordinate translation transformation $x^{t} \rightarrow x^{1}=x^{t},$ where $\alpha^{t}$ is a constant $3-$ vector. Then, show the same result via commutation of the three-momentum operator.

\textbf{Solution}
The Lagrangian density is $\mathcal{L}_{0}^{0}=\phi_{, \mu}^{\dagger} \phi^{\mu}-\mu^{2} \phi^{\dagger} \phi .$ We must integrate this over all volume to get the total Lagrangian $L$. If $k_{i}$ is conserved, then of course, so is $k^{i}$. So, we need to show $L$ is invariant under $x^{i} \rightarrow x^{i}=x^{i}+\alpha^{i}$
$$
\phi=\sum_{\mathbf{k}} \frac{1}{\sqrt{2 V a_{\mathbf{k}}}}\left(a(\mathbf{k}) e^{-i k_{\mu} x^{\mu}}+b^{\dagger}(\mathbf{k}) e^{i k_{\mu} x^{\mu}}\right) \quad \phi^{\dagger}=\sum_{\mathbf{k}} \frac{1}{\sqrt{2 V a_{k}}}\left(b(\mathbf{k}) e^{-i k_{\mu} x^{\mu}}+a^{\dagger}(\mathbf{k}) e^{i k_{\mu} x^{\mu}}\right)
$$
$$
\begin{array}{l}
{\phi_{s}, \mu=\sum_{\mathbf{k}} \frac{i k_{\mu}}{\sqrt{2 V \omega_{\mathbf{k}}}}\left(-a(\mathbf{k}) e^{-i k_{\mu} x^{\mu}}+b^{\dagger}(\mathbf{k}) e^{i k_{\mu} x^{\mu}}\right)} \\
{\phi^{, \mu}=\sum_{\mathbf{k}} \frac{i k^{\mu}}{\sqrt{2 V a_{k}}}\left(-a(\mathbf{k}) e^{-i k_{\mu} x^{\mu}}+b^{\dagger}(\mathbf{k}) e^{i k_{\mu} x^{\mu}}\right)}
\end{array}
$$
$$
\begin{aligned}
\phi^{\dagger}_{z \mu} \phi^{z}=\sum_{\mathbf{k}} \sum_{\mathbf{k}^{*}} \frac{-1}{2 V} \frac{k_{\mu} k^{* \mu}}{\sqrt{\omega_{\mathbf{k}} \omega_{\mathbf{k}^{*}}}}\left(b(\mathbf{k}) a\left(\mathbf{k}^{*}\right) e^{-i k_{A} x^{\mu}} e^{-i k_{A}^{*} x^{\mu}}-b(\mathbf{k}) b^{\dagger}\left(\mathbf{k}^{*}\right) e^{-i k_{\mu} x^{\mu}} e^{i k_{\mu} x^{\mu}}\right.\\
-a^{\dagger}(\mathbf{k}) a\left(\mathbf{k}^{*}\right) e^{i k_{\mu} x^{\mu}} e^{-i k_{\mu} x^{\mu}}+a^{\dagger}(\mathbf{k}) b^{\dagger}\left(\mathbf{k}^{*}\right) e^{i k_{\mu} x^{\mu}} e^{i k_{\mu} x^{\mu}}
\end{aligned}
$$
For $k_{i}=-k^*_i$, we have $$
\left.k_{\mu} k^{* \mu}=\omega_{\mathbf{k}}^{2}+k_{i} k^{*i}=\omega_{\mathbf{k}}^{2}+k_{i}\left(-k^{i}\right)=\omega_{\mathbf{k}}^{2}+k_{i} k_{i}=k_{\mu} k_{\mu}\right.
$$
$$
\int \phi^{\dagger}_{,\mu} \phi^{, \mu} d V=\sum_{k} \frac{-1}{2 \omega_{k}}\left(\begin{array}{c}
{k_{\mu} k_{\mu} e^{-i 2 \omega_{k} t} b(\mathbf{k}) a(-\mathbf{k})-k_{\mu} k^{\mu} b(\mathbf{k}) b^{\dagger}(\mathbf{k})} \\
{-k_{\mu} k^{\mu} a^{\dagger}(\mathbf{k}) a(\mathbf{k})+k_{\mu} k_{\mu} e^{i 2 \omega_{k} t} a^{\dagger}(\mathbf{k}) b^{\dagger}(-\mathbf{k})}
\end{array}\right)
$$
Similarly,
$$
\int \mu^{2} \phi^{\dagger} \phi d V=-\sum_{\mathbf{k}} \frac{\mu^{2}}{2 \omega_{\mathbf{k}}}\left(e^{-i 2 \omega_{\mathbf{k}} t} b(\mathbf{k}) a(-\mathbf{k})+b(\mathbf{k}) b^{\dagger}(\mathbf{k})+a^{\dagger}(\mathbf{k}) a(\mathbf{k})+e^{i 2 \omega_{\mathbf{k}} t} a^{\dagger}(\mathbf{k}) b^{\dagger}(-\mathbf{k})\right)
$$
It is easy to show that, after the transformation the forms of $\int \mu^{2} \phi^{\dagger} \phi d V$ and $\int \phi^{\dagger}_{,\mu} \phi^{, \mu} d V$ will not change, so L is symmetric in some coordinate, then the conjugate momentum of that coordinate is conserved. $k_{i}$, the particle(s) 3 -momentum is the conjugate momentum of $x^{i} .$ Thus, $k_{i}$, is conserved.

Also
$$
H=\sum_{\mathbf{k}} \omega_{\mathbf{k}}\left(N_{a}(\mathbf{k})+N_{b}(\mathbf{k})\right) \quad \mathbf{P}=\sum_{\mathbf{k}} \mathbf{k}\left(N_{a}(\mathbf{k})+N_{b}(\mathbf{k})\right) \rightarrow[H, \mathbf{P}]=0 \quad\left(\begin{array}{ll}
{\text { because all number }} \\
{\text { operators commute }}
\end{array}\right)
$$
Thus $\mathbf{P}$ is conserved for the free Hamiltonian.